---
title: "tutorial"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(testpackage)
library(stats)
library(ggplot2)
```

To construct a linear regression model using demo_data
```{r}
m = lm(fev~A+H+M+S, data = demo_data)
```

To test whether maximum leverage is the same from `hat_matrix` and `hatvalues` manualy
```{r}
h = hatvalues(m)
all.equal(as.numeric(hat_matrix(m)[1]), unname(h[which.max(h)]))
bench::mark(as.numeric(hat_matrix(m)[1]), unname(h[which.max(h)]))
plot(bench::mark(mine = as.numeric(hat_matrix(m)[1]), original = unname(h[which.max(h)])))
```


Benchmark `res_3` and `rstandard` for computing internally studentized residuals
```{r}
all.equal(rstandard(m),res_3(demo_data, m, r = "int"))
int_bench = bench::mark(original = rstandard(m),mine = res_3(demo_data, m, r = "int"))
print(int_bench)
plot(int_bench)
```

Benchmark `res_3` and `rstandard` for computing externally studentized residuals
```{r}
all.equal(rstudent(m),res_3(demo_data, m, r = "ex"))
ex_bench = bench::mark(original = rstudent(m),mine = res_3(demo_data, m, r = "ex"))
print(ex_bench)
plot(ex_bench)
```


Benchmark `outlier_influence` and `diffits` for computing DFFITS
```{r}
all.equal(dffits(m),outlier_influence(demo_data, m, option = c("dffits")))
result_ff = bench::mark(original = dffits(m),mine = outlier_influence(demo_data, m, option = c("dffits")))
print(result_ff)
plot(result_ff)
```

Becnhmark `outlier_influence` and `cooks.distance` for computing Cook's distance
```{r}
all.equal(outlier_influence(demo_data, m, option = "cd"), cooks.distance(m))
result_cd = bench::mark(mine = outlier_influence(demo_data, m, option = "cd"), original = cooks.distance(m))
print(result_cd)
plot(result_cd)
```

Benchmark `outlier_influence` and `covratio` for computing COVRATIO
```{r}
all.equal(outlier_influence(demo_data, m, option = c("cvr")), covratio(m))
result_cvr = bench::mark(mine = outlier_influence(demo_data, m, option = c("cvr")), original = covratio(m))
print(result_cvr)
plot(result_cvr)
```


Demostration on `plot_dffits` , `plot_cd`, and `plot_CVR`
```{r}
plot_dffits(m)
plot_cd(m)
plot_CVR(m)
```

